\section{Simplicial Homology}

\textbf{Notation:}

Let $f, g$ be partial functions from the set $X$ to set $Y$: $\dom(f) \cap \dom(g) = \emptyset$ then
\begin{equation*}
  f \frown g: \dom(f) \cup \dom(g) \to Y, \: x \mapsto \begin{cases}
    f(x), \: x \in \dom(f), \\
    g(x), \: x \in \dom(g).
  \end{cases}
\end{equation*}

\subsection{Abstract simplicial complexes}

\begin{defin}
    Let $X$ be a non-empty set. Then a collection $\mathcal{K} \subseteq \PowSF(X)$ of finite subsets of $X$ is called a 
    \textbf{simplicial complex} of $X$ if
    \begin{itemize}
        \item $\bigcup \mathcal{K} = X$,
        \item $\forall \sigma\in\mathcal{K} \colon \tau \subseteq \sigma \; \Rightarrow \; \tau \in \mathcal{K}$.
    \end{itemize}
    The elements of the set $V(\mathcal{K}) := \bigcup \mathcal{K}$ are the \textbf{vertecies} of $\mathcal{K}$ and
    elements of $\mathcal{K}$ itself are the \textbf{simplicies}. Given a simplex $\sigma \in \mathcal{K}$ then the sets
    $\; \sigma \setminus \{x\} \;$ for $x \in \sigma$ are called the \textbf{faces} of $\sigma$.

    Let $\sigma \in \mathcal{K}$ then $\dim \sigma = |\sigma| -1$ is the \textbf{dimension} of $\sigma$. The dimension of $\mathcal{K}$ is
    \begin{equation*}
      \dim \mathcal{K} = \max\{\dim \sigma\colon \sigma \in \mathcal{K}\}.
    \end{equation*} 
    
    Let $Y$ be another non-empty set and $\mathcal{L}$ be a simplicial complex on $Y$. A map $f: V(\mathcal{K}) \to V(\mathcal{L})$ is called 
    a \textbf{simplicial} map if
    \begin{equation*}
        \forall \sigma \in \mathcal{K}\colon f(\sigma) \in \mathcal{L}.
    \end{equation*}
    If $f$ is bijective and $f^{-1}\colon \mathcal{L} \to \mathcal{K}$ is a simplicial map then $f$ is an \textbf{combinatorial isomorphism}.
\end{defin}

% Simple example of a simplicial complex
\begin{ex}\label{ex:seqcom}
  Let $n \in \N^+$ then $\mathcal{K}_n$ defined as
  \begin{equation*}
    \mathcal{K}_n = \PowS([n])
  \end{equation*}
  is a sequence of simplicial complexes. For example $\mathcal{K}_2 := \{\emptyset, \{0\}, \{1\}, \{0,1\}\}$.
\end{ex}

\begin{defin}
    Let $X$ be a set, $H$ be a group and $\mathcal{K}$ be a simplicial complex on $X$. If there is an 
    group action $\lambda \colon H \times X \to X$ of $H$ on $X$ then
    the complex $\mathcal{K}$ is an \textbf{$H$-complex} if the map
    \begin{equation*}
        \lambda_h \colon \mathcal{K} \to \mathcal{K}, \: \sigma \mapsto \{ \lambda(h, \tau)\colon \tau \in \sigma \}
    \end{equation*}
    is a simplicial map for all $h \in H$.
\end{defin}

% TODO: put this in the appendix
\begin{defin}
    A poset (partially ordered set) is a pair $(P, \preceq)$ where 
    $P$ is a non-empty set and 
    $\preceq$ is a binary relation on $P$ which has the following properties:
    \begin{enumerate}
        \item \textit{Reflexivity}: $\forall x \in P\colon x \preceq x$,
        \item \textit{Antisymmetry}: $\forall x, y \in P\colon (x \preceq y \: \land \: y \preceq x) \Rightarrow (x = y)$,
        \item \textit{Transitivity}: $\forall x, y, z \in P\colon (x \preceq y \: \land \: y \preceq z) \Rightarrow (x \preceq z)$.
    \end{enumerate}
    A chain in $P$ is a subset $C \subseteq P$ which is totally ordered, i.e.
    \begin{equation*}
        \forall x, y \in C\colon x \preceq y \: \lor \: y \preceq x.
    \end{equation*}
\end{defin}

\begin{ex}
    If $X$ is a non-empty set then the pair $(\PowS(X), \subseteq)$ forms a poset.
\end{ex}

The last example establishes the following definition:
If $X$ is a non-empty family of sets then $P(X) := (X, \subseteq)$ is the poset generated by $X$. The elements of $X$
are the elements of the poset and the binary relation of set inclusion is the partial order.

\begin{defin}
    Let $\mathcal{K}$ be an abstract simplicial complex. The \textbf{barycentric subdivision} $\sd(\mathcal{K})$ of $\mathcal{K}$
    is the abstract simplicial complex with $\mathcal{K}$ as the set of vertecies and all chains in $P(\mathcal{K})$ as simplicies.
\end{defin}

\begin{thm}
    If $\mathcal{K}$ is a abstract simplicial complex, then $\sd(\mathcal{K})$ is a well-defined abstract simplicial complex.
\end{thm}

\begin{proof}
    Let $\sigma \in \sd(\mathcal{K})$. Now let $\tau \subseteq \sigma$. Since $\sigma$ was totally ordered $\tau$ is also totally ordered.
    This means that $\tau \in \mathcal{K}$.
\end{proof}

% TODO: example of barycentric subdivision of the triangle simplex 1,2,3

We need a way to turn an abstract simplicial complex into a geometric structure such that it can be analyzed with the tools provided by algebraic topology. This means that there should be a map from the simplicies of the abstract complex to $n$-dimensional euclidian space. This map is called the \textbf{geometric realization} of the abstract simplicial complex which maps it to a geometric simplicial complex. 
These geometric complexes consist of polyhedra. They are constructed by "gluing" 
together points, straight line segments, polyhedra and their higher dimensional generalizations.
It will be clear that these two types of objects internally encode the same combinatorical structure. 

\begin{defin}
    Let $n,k \in \N$ and let $x_0, x_1, \ldots, x_k \in \R^n$. The vectors $x_i$ are called \textbf{linearly independent} if it holds that 
    \begin{equation*}
        \sum\limits_{i=0}^k \alpha_i x_i = 0 \; \iff \; \alpha_0 = \alpha_1 = \ldots = \alpha_k = 0,
    \end{equation*} with $\alpha_j \in \R$ and $j = 0, 1, \ldots, k$.
    The vectors are called \textbf{affinely independent} if
    \begin{equation*}
        \sum\limits_{i=0}^k \alpha_i = 0 \; \land \; \sum\limits_{i=0}^k \alpha_i x_i = 0 \; \Rightarrow \; \alpha_0 = \alpha_1 = \ldots = \alpha_k = 0, 
    \end{equation*} with $\alpha_j \in \R$ and $j = 0, 1, \ldots, k$.
\end{defin}

\begin{defin}
    Let $n,k \in \N$ and let $x_0, x_1, \ldots, x_k \in \R^n$. The convex hull of the vectors $x_i$ is
    \begin{equation*}
        {\rm co} (A) = {\rm co}(x_0, x_1, \ldots, x_k) := \{ t_0 x_0 + t_1 x_1 + \cdots + t_k x_k \colon t_i \in [0, 1], \sum\limits_{i=0}^k t_i = 1\}
    \end{equation*}
    where $A = \{x_i\colon i \in [k]\}$.  
\end{defin}

\begin{rem}
  Let $d\in\N$ and $A,B \subseteq \R^d$. If $A \cup B$ affinely independent, then
  \begin{equation*}
    ({\rm co} A) \cap ({\rm co}B) = {\rm co}(A \cap B).
  \end{equation*}
\end{rem}

Affine independence of the vectors makes sure that the convex hull of vectors is not degenerated.
For example it is expected that the convex hull of three vectors in $\R^2$ is a triangle. But in the degenerate case that the points are all the same
or the points lie in a straight line, this is not true. When it is assumed that the points are affinely independent, these cases are excluded. 

\begin{defin}
  A \textbf{geometric realization} of an abstract simplicial complex $\mathcal{K}$ is a map
  \begin{equation*}
    f\colon V(\mathcal{K}) \to \R^d
  \end{equation*}

  with $d \in \N$ such that
  \begin{enumerate}
    \item $\forall \sigma \in \mathcal{K}\colon f(\sigma)$ affinely independent,
    \item $\forall \sigma_1, \sigma_2\in \mathcal{K}\colon ({\rm co}f(\sigma_1)) \cap ({\rm co} f(\sigma_2)) = {\rm co}f(\sigma_1 \cap \sigma_2)$.
  \end{enumerate}
    Given a geometric realization $f$ for $\mathcal{K}$, then $\lVert K \rVert_f = f(\mathcal{K})$. The symbol $\lVert \mathcal{K} \rVert$ refers the an arbitrary geometric realization of $\mathcal{K}$ in the smallest dimension $d$ that is possible.
    Let $x \in \lVert K \rVert_f$. Then $x$ is in ${\rm co}A_x$ for exactly one set $\{f(v_1), f(v_2), \ldots, f(v_k)\} = A_x \subseteq f(V(\mathcal{K}))$ for which the following equations hold 
    \begin{equation*}
      x = \sum\limits_{i=1}^k t_i \cdot f(v_i), \hspace*{30px} \sum\limits_{i=1}^k t_i = 1, 
    \end{equation*}
    where $k\in \N^+$ and $t_i \in [0, 1]$ for all $i \in \{1, 2, \ldots, k\}$. Define $\alpha_v(x)$ as
    \begin{equation*}
      \alpha_v(x) = \begin{cases}
        &t_i, \: v \in A_x, \\
        &0, \: \text{otherwise}
      \end{cases}
    \end{equation*}
    for $v \in V(\mathcal{K})$.
\end{defin} 

To show that $\lVert \mathcal{K} \rVert$ for an abrbitrary simplicial complex is well-defined, we need the following theorem.

\begin{thm}
  Let $\mathcal{K}$ be a simplicial complex with $\dim \mathcal{K} = n \in \N$. Then there exists a geometric realization $f\colon V(\mathcal{K}) \to \R^{2d+1}$.
\end{thm}

\begin{proof}
  This is a direct consequence of \cite[Lemma 5.1.1]{using2003}.
\end{proof}

\begin{defin}
  Let $d \in \N^d$ and let $f\colon V(\mathcal{K}) \to \R^d$. The \textbf{affine extension} $\lVert f \rVert$ of this function is defined as
  \begin{equation*}
    \lVert f \rVert\colon \lVert \mathcal{K} \rVert \to \R^d,\: x \mapsto \sum\limits_{v \in V(\mathcal{K})} \alpha_v(x) f(v).
  \end{equation*}
\end{defin}

% TODO: add pictures for the geometric realizations
% TODO: prove of the last statement in this example
\begin{ex}
  Take the sequence of simplicial complexes $\mathcal{K}_n$ from example \ref{ex:seqcom}. A possible geometric realization of these complexes is
  \begin{equation*}
    f_n\colon V(\mathcal{K}_n) \to \R^n, k \mapsto e_k 
  \end{equation*}
  where $e_k$ for $k \in [n]$ is the $k$-th canonical basis vector of $\R^n$. This sequence of complexes have the property that there is a homeomorphism $\psi\colon \lVert \mathcal{K}_n \rVert_f \to \mathbb{S}^{n-1}$.
\end{ex}

\begin{defin}
  Let $\mathcal{K}$ and $\mathcal{L}$ be abstract simplicial complexes. The \textbf{join} of these complexes is defined as
  \begin{equation*}
    \mathcal{K} \star \mathcal{L} := \{\sigma \sqcup \tau\colon \sigma \in \mathcal{K}, \tau \in \mathcal{L} \}.
  \end{equation*}
  The special case ${\rm Cone}(\mathcal{K}) = \mathcal{K} \star \{ \Delta \}$ is the cone of $\mathcal{K}$ with a cone point $\Delta$. 
  Now define basepoints $v_k \in V(\mathcal{K}), v_l \in V(\mathcal{L})$ of the two simplicial complexes. The \textbf{wedge} of $\mathcal{K}$ with $\mathcal{L}$ is defined as
  \begin{equation*}
    \mathcal{K} \lor \mathcal{L} := \: \faktor{\mathcal{K} \sqcup \mathcal{L}}{\sim}
  \end{equation*}
  where $\sim$ is the equivalence relation, that identifies the basepoints.
  The $n$-fold wedge is the $n$-fold disjoint union with the same equivalence relation.
\end{defin}

\begin{ex}
  Let $\mathcal{K} = \mathcal{L} = \mathcal{K}_2$ from example \ref{fig:simwe} and choose the basepoints $1 \in V(\mathcal{K}), 1 \in V(\mathcal{L})$. Then a geometric realization of the wedge $\mathcal{K} \lor \mathcal{L}$ is depicted in the figure \ref{ex:simwejo}.
  \begin{figure}[h!]
    \centering
    \begin{tikzpicture}
\node[fill=black, circle, inner sep=2pt, label=below:{$0$}] (A) at (0,0) {};
\node[fill=black, circle, inner sep=2pt, label=below:{$2$}] (B) at (2,0) {};
\node[fill=black, circle, inner sep=2pt, label=above:{$1$}] (C) at (1,2) {};
\node[align=center] at (1,-0.5) (label1) {$\mathcal{K}$};

\node[fill=black, circle, inner sep=2pt, label=below:{$0$}] (D) at (3,0) {};
\node[fill=black, circle, inner sep=2pt, label=below:{$2$}] (E) at (5,0) {};
\node[fill=black, circle, inner sep=2pt, label=above:{$1$}] (F) at (4,2) {};
\node[align=center] at (4,-0.5) (label2) {$\mathcal{L}$};

\node[fill=black, circle, inner sep=2pt, label=above:{$0$}] (G) at (9,2) {};
\node[fill=black, circle, inner sep=2pt, label=below:{$2$}] (H) at (9,0) {};
\node[fill=black, circle, inner sep=2pt, label=above:{$1$}] (I) at (11,1) {};
\node[fill=black, circle, inner sep=2pt, label=above:{$2$}] (J) at (13,2) {};
\node[fill=black, circle, inner sep=2pt, label=below:{$0$}] (K) at (13,0) {};
\node[align=center] at (11,-0.5) (label3) {$\mathcal{K} \lor \mathcal{L}$};

\node at (5.5, 1) (AS) {};
\node at (8.5, 1) (AE) {};

\draw (A) -- (B);
\draw (B) -- (C);
\draw (C) -- (A);

\draw (D) -- (E);
\draw (D) -- (F);
\draw (E) -- (F);

\draw (G) -- (I);
\draw (G) -- (H);
\draw (H) -- (I);
\draw (J) -- (K);
\draw (J) -- (I);
\draw (K) -- (I);

\draw [->, thick] (AS) -- node[above] {$\lor$} (AE);
    \end{tikzpicture} 
    \caption{Examples of the wedge of simplicial complexes.}\label{fig:simwe}
\end{figure}

Now consider the complexes $\mathcal{K} = \PowS_{1}(\{0, 1\})$ and $\mathcal{L} = \PowS_1(\{2, 3\})$. The geometric realization of the join $\mathcal{K} \star \mathcal{L}$ of these complexes can be seen in figure \ref{fig:simjo}. From the figure it becomese apperent that $\lVert \mathcal{K} \star \mathcal{L} \rVert$ is homeomorphic to $\mathbb{S}^1$.

  \begin{figure}[h!]
  \centering
  \begin{tikzpicture}
\node[fill=black, circle, inner sep=2pt, label=below:{$0$}] (D) at (1,0) {};
\node[fill=black, circle, inner sep=2pt, label=below:{$1$}] (E) at (2,0) {};
\node[align=center] at (1.5,-1) (label3) {$\mathcal{K}$};

\node[fill=black, circle, inner sep=2pt, label=below:{$2$}] (D) at (2,2) {};
\node[fill=black, circle, inner sep=2pt, label=below:{$3$}] (E) at (3,2) {};
\node[align=center] at (2.5,1) (label3) {$\mathcal{L}$};

\node[fill=black, circle, inner sep=2pt, label=above:{$0$}] (G) at (7,2) {};
\node[fill=black, circle, inner sep=2pt, label=below:{$3$}] (H) at (7,0) {};
\node[fill=black, circle, inner sep=2pt, label=above:{$2$}] (I) at (9,2) {};
\node[fill=black, circle, inner sep=2pt, label=below:{$1$}] (K) at (9,0) {};
\node[align=center] at (8,-0.5) (label3) {$\mathcal{K} \star \mathcal{L}$};

\node at (4, 1) (AS) {};
\node at (6, 1) (AE) {};

\draw (G) -- (H);
\draw (H) -- (K);
\draw (K) -- (I);
\draw (I) -- (G);

\draw [->, thick] (AS) -- node[above] {$\star$} (AE);
  \end{tikzpicture}
  \caption{Example of the join of simplicial complexes.}\label{fig:simjo}
  \end{figure}
\end{ex}

The fact that the join of a two points with two points results in a simplicial complex that has a geometric realization that is homeomorphic does not only work with $\mathbb{S}^1$. This fact holds more generally for the n-fold join of 2-point simplicial complexes. 

\begin{lemma}
  Let $\mathcal{K}_n := \PowS_1(\{(0, n), (1, n)\})$ for $n \in \N^+$, then
  \begin{equation*}
    \left\lVert \bigstar_{i=1}^k \mathcal{K}_i \right\rVert \: \cong \: \mathbb{S}^{k-1}.
  \end{equation*}
\end{lemma}

% TODO: finish proof or search for source of proof
\begin{proof}
  - define $f_n$ realization inductively
  - proof that polyhedra are triangulation of sphere
\end{proof}

% Universal coefficient theorem
% Alexanders Duality
% Mayer Vietoris Sequence
\subsection{Homology Theory}
Now a very important tool in algebraic topology is introduced, namely \textbf{Homology Theory} of topological spaces. For the definitions from Category theory used in this section look at Appendix \ref{}. 

\begin{cons}
  Let $S$ be a finite set and $p \in \mathbb{P}$. Define \[A(S) := \{f \in \Z^S\colon |\im f| < \infty \}\] be maps from $S$ to $Z_p$ with finite image. $A(S)$ is an abelian group together with the operation of pointwise addition of maps.
  Then the set \[\{\mathds{1}_x\colon x\in S\} \subseteq A(S)\] forms a basis of the abelian group $A(S)$.
  Let $T$ be another set. For a map $\varphi\colon S \to T$ define the map $A(T; p)$ as
  \begin{equation*}
    A(\varphi)\colon A(S) \to A(T),\; f \mapsto \sum\limits_{x \in S}f(x)\cdot \mathds{1}_{\varphi(x)}.
  \end{equation*}
  This map is a homomorphisms of abelian groups.
\end{cons}

\begin{proof} 
  The fact that $A(S)$ is abelian follows from the fact that the group $\Z$ is abelian and thus the pointwise addition is associative and commutative, the neutral element is the constant $0$ function and the inverse of an element $f \in A(S)$ is defined as $f^{-1}(s) = -f(s)$ for $s \in S$.

  Now let $f \in A(S)$ and consider the function \[\tilde{f}\colon S \to \Z, \: s \mapsto \sum\limits_{x\in S} \alpha_x \mathds{1}_x(s)\] with $\alpha_x = f(x)$ for all $x \in S$. Let $s \in S$. It follows that
  \begin{equation*}
    \tilde{f}(s) = \sum\limits_{x \in S} \alpha_x \mathds{1}_x(s) = \alpha_s = f(s).
  \end{equation*}

  Now let $f,g \in A(S)$.
  \begin{align*}
    A(\varphi)(f+g^{-1}) &= \sum\limits_{x\in S} (f+g^{-1})(x)\cdot \mathds{1}_{\varphi(x)} \\
                        &= \sum\limits_{x\in S} (f(x)-g(x)))\cdot \mathds{1}_{\varphi(x)} \\
                        &= \sum\limits_{x\in S} f(x)\cdot\mathds{1}_{\varphi(x)} + (-g(x))\cdot \mathds{1}_{\varphi(x)} \\
                        &= \sum\limits_{x\in S} f(x)\cdot\mathds{1}_{\varphi(x)} + \sum\limits_{x\in S} (-g(x))\cdot \mathds{1}_{\varphi(x)} \\
                        &= A(\varphi)(f) + A(\varphi)(g)^{-1}.  
  \end{align*}
\end{proof}

Since the collection of indicator functions is a basis of $A(S)$ it is a convention to write elements of $A(S)$ as formal linear combinations of elements of the generating set $S$. This means the group $A(S)$ can also be represented as
\begin{equation*}
  A(S) = \left\{\sum\limits_{i=1}^k r_i x_i\colon k\in \N, \: \forall i \in \{1, \ldots, k\}\colon x_i \in S, r_i \in \Z\right\}.
\end{equation*}

\begin{thm}\label{thm:isoab}
  Let $S$ be a set and let $B$ be an abelian group. Then \[\Phi\colon \underline{\rm Ab}(A(S), B) \to B^X, \: \varphi \mapsto\varphi \circ \mathds\iota^S\footnote{$\iota^S\colon S \to A(S), \: s \mapsto \mathds{1}_s$}\] is a bijection.
\end{thm}

\begin{proof}
  The map $\Phi$ is a homomorphism in of abelian groups. To this end let $\varphi, \psi \in \underline{\rm Ab}$.
  The claim follows from the fact that $\varphi$ and $\psi$ are homomorphisms and \[(\varphi + \psi)(\mathds{1}_x) = \varphi(\mathds{1}_x) + \psi(\mathds{1}_x).\]
  Let $\varphi \in \underline{\rm Ab}(A(S), B)$ and assume that $\varphi \circ \iota^S = 0$. Then it holds that
  \begin{align*}
    \varphi(f) &= \varphi\left(\sum\limits_{x \in S}f(x) \cdot \mathds{1}_s\right) \\
    &= \sum\limits_{x \in S} f(x) \cdot \varphi(\mathds{1}_s) \\
    &= \sum\limits_{x \in S} f(x) \cdot 0 = 0
  \end{align*}
  for all $f \in A(S)$ and thus $\varphi = 0$. This means $\ker \Phi = \{0\}$.
  Now let $\psi \in B^S$. Then the map \[\xi\colon A(S) \to B, f \mapsto \sum\limits_{x \in S} f(x) \psi(x) \] is a homomorphism by
  \begin{align*}
    \xi(f + g) &= \xi\left(\sum\limits_{x \in S} (f+g)(x) \mathds{1}_x\right) \\
    &= \sum\limits_{x \in S}(f+g)\psi(x) \\
    &= \sum\limits_{x \in S} f(x)\psi(x) + \sum\limits_{x \in S}g(x)\psi(x) = \xi(f) + \xi(g).
  \end{align*}
  And now it follows that $\Phi(\xi) = (\xi \circ \iota^S)(x) = \mathds{1}_x(x) \cdot \psi(x) = \psi(x)$ for all $x \in X$ and hence $\Phi(\xi) = \psi$.
\end{proof}

The Theorem now tells us that any function from $X$ to an abelian group $B$ can be extended into a function from $A(X)$ to $B$ in a unique way. This may become clear looking at the commutative diagram in figure \ref{fig:com1}.

\begin{figure}[h!]
  \centering
  % https://tikzcd.yichuanshen.de/#N4Igdg9gJgpgziAXAbVABwnAlgFyxMJZABgBpiBdUkANwEMAbAVxiRAA0QBfU9TXfIRQBGUsKq1GLNgCFuvEBmx4CRMuOr1mrRCACCACnYBKbhJhQA5vCKgAZgCcIAWyRkQOCEgBM1HHSwGNgALCAgAaxBqBiwwHRA4CBioKJBgmDoUxDAmBgZougAjGAYABX4VIRAHLEtgnFStaV0AHRb8fwA9Tmo4YKw7BsRiHnsnV2G-L0RRSW02NvoHNH75MZcfKaRZmLi2KAgcHAtUhiKS8uVBNhq6hs0peLaYAA8sOBw4AEI24LocYCLOjLfpcMxcIA
  \begin{tikzcd}
    X \arrow[d, "\iota^X"', hook] \arrow[rd, "\varphi"] &   \\
    A(X) \arrow[r, "\exists!\hat{\varphi}"', dashed]    & B
  \end{tikzcd}
  \caption{Commutative diagram showing the statement of Theorem \ref{thm:isoab}}\label{fig:com1}
\end{figure}

\begin{defin}
  Let $n\in\N$. The \textbf{geometric n-simplex} $\Delta_n$ is defined as
  \begin{equation*}
    \Delta_n := {\rm co}\{e_0\, \ldots, e_n\} \subseteq \R^{n+1}
  \end{equation*}
  where $e_i$ is the $i$-th canonical basis vector of $R_n$ for $i = 0,\ldots,n$. For all $i = 0, \ldots, n$ define the $i$-th face map as
  \begin{equation*}
    d_i\colon \Delta_{n-1} \to \Delta_n,\: (t_0,\ldots,t_{n-1}) \mapsto (t_0, \ldots, t_{i-1}, 0, t_i, \ldots, t_{n-1}).
  \end{equation*}
  Notice that $\im d_i \subseteq \Delta_n$. $\im d_i$ is called the $i$-th face of $\Delta_n$.
\end{defin}

\begin{defin}
  Let $X$ be a topological space and let $n\in \N$ and $p \in \mathbb{P}$. A \textbf{singular $n$-simplex} in $X$ is a continuous map $\sigma \in \underline{\rm Top}(\Delta_n, X)$.
  Now the \textbf{singular $n$-chain group} of $X$ is defined as $C_n(X) := A(\underline{\rm Top}(\Delta_n, X); p)$. An element $\sigma \in C_n(X)$ is called a singular $n$-chain in $X$.
  The map \[\partial_n\colon C_n(X) \to C_{n-1}(X),\: \sigma \mapsto \sum\limits_{i=0}^n(-1)^i(\sigma \circ d_i)\] is called the $n$-th boundary map for $n\in\N^+$. It is a homomorphisms of abelian groups. For $n < 1$ define $\partial_n$ as the zero map as well as all $C_n$ as trivial abelian groups.

  If $Y$ is another topological space and $f \in \underline{\rm Top}(X, Y)$ then $C_n(f)\colon C_n(X) \to C_n(Y)$ defined on the generators $\sigma \in C_n(X)$ as
  \begin{equation*}
    C(f)(\sigma) = f \circ \sigma.
  \end{equation*}
  This map is a homomorphism of abelian groups.
\end{defin}

\begin{lemma}
  The composition $\partial_n \circ \partial_{n+1} = 0$ for all $n \in \N$.
\end{lemma}

\begin{proof}
  See \cite[Theorem 29.1]{MunAlTop}.
\end{proof}

The lemma above is the so called fundamental theorem of homology theory. It allows for the following definition.

\begin{defin}
  Let $X$ be a topological space, then \[C_\bullet(X) := ((C_n(X))_{n\in \Z}), (\partial_n)_{n\in \Z})\] with
  \[C_n(X) = \{0\}, \: \partial_n := 0\] for $n \in \Z\setminus\N$ is a chain complex.
\end{defin}

\begin{lemma}
  Let $X, Y$ be topological spaces and $f \in \underline{\rm Top}(X, Y)$, then \[\forall n\in \N\colon \partial_n \circ C_n(f) = C_{n-1}(f) \circ \partial_n.\]
\end{lemma}

\begin{proof}
  Let $n \in \N^+$ and let $\sigma \in \underline{\rm Top}(\Delta_n, X)$ then
  \begin{align*}
    \partial_n(C_n(f)(\sigma)) &= \partial_n(f\circ\sigma) \\
    &= \sum\limits_{i=0}^n(-1)^if\circ\sigma\circ d_i \\
    &= \sum\limits_{i=0}^n(-1)^iC_{n-1}(f)(\sigma\circ d_i) \\
    &= C_{n-1}(f)(\sum\limits_{i=0}^n(-1)^i(\sigma\circ d_i)) \\
    & = C_{n-1}(f)(\partial_n(\sigma)).
  \end{align*}
\end{proof}

From the previous lemma it is clear that $C_\bullet(f) := (C_n(f))_{n\in \Z}$ with $C_n(f) = 0$ for $n < 0$ is a homomorphism between chain complexes $C_\bullet(X)$ and $C_\bullet(Y)$.

\begin{lemma}\label{lem:cfunc}
  $C_\bullet\colon \underline{\rm Top} \to \underline{\rm C}(\underline{\rm Ab})$ is a functor.
\end{lemma}

\begin{proof}
  Let $X$ be a topological space and let $n \in \N$, then \[C_n(\id_X)(\sigma) = \id_X\circ \sigma = \sigma = \id_{C_n(X)}(\sigma)\]
  for all $\sigma \in \underline{\rm Top}(\Delta_n, X)$ and hence $C_n(\id_X) = \id_{C_n(X)}$.
  For $n < 0$ this is trivial.

  Let $Y, Z$ be topological spaces and $f \in \underline{\rm Top}(X, Y), g\in \underline{\rm Top}(Y, Z)$, then for $n\in \N$ it follows that \[C_n(g\circ f)(\sigma) = g\circ f \circ \sigma = C_n(g)(f\circ \sigma) = (C_n(g) \circ C_n(f))(\sigma)\] for all $\sigma \in \underline{\rm Top}(\Delta_n, X)$ and thus $C_n(g \circ f) = C_n(g) \circ C_n(f)$.
  Again the case for $n < 0$ is trivial.
\end{proof}

\begin{thm}\label{thm:hfunc}
  Let $n \in \N$. Then \[H_n\colon \underline{\rm Top} \to \underline{\rm Ab} \]
  defined by \[H_n(X) := H_n(C_\bullet(X)), \: H_n(f) := H_n(C_\bullet(f))\]
  for a topological spaces $X$ and $Y$ and $f \in \underline{\rm Top}$ is called the $n$-th singular homology group and  is a functor. 
\end{thm}

\begin{proof}
  Follows from the fact that the composition of functors is again a functor and Theorem \ref{}.
\end{proof}

\begin{thm}\label{thm:hhom}
  Let $X$ and $Y$ be topological spaces. Then if $f, g\in \underline{\rm Top}(X, Y)$ are homotopic maps it follows that \[H_n(f) = H_n(g)\] for all $n \in \N$.
\end{thm}

\begin{proof}
  See \cite[p. 112f]{hatcher}.
\end{proof}

\begin{col}
  Let $X$ and $Y$ be topological spaces and $f \in \underline{\rm Top}(X, Y)$ is a homotopy equivalence between them, then $H_n(f)\colon H_n(X) \to H_n(Y)$ is an isomorphism for all $n \in \Z$.
\end{col}

\begin{proof}
  This follows directly from Theorem \ref{thm:hhom}.
\end{proof}

\begin{proof}
  Since $f$ is a homotopy equivalence $f$ is a bijection. This means that there is $f^{-1}\colon Y \to X$ and thus $H_n(f^{-1})\colon H_n(Y) \to H_n(X)$. Now with Theorem \ref{thm:hfunc} it follows that 
  \begin{align*}
    H_n(f) \circ H_n(f^{-1}) = H_n(f \circ f^{-1}) = H_n(\id_X) = \id_{H_n(X)}.
  \end{align*}
\end{proof}

\begin{ex}
  Take a topological space $X$. Then $H_0(X) \cong \Z^n$ where $n \in \N$ is the number of path-connected components in $X$. 
\end{ex}

The example above implies that the $0$-th homology group of for example a one point space is $\Z$. This complicates some other results in homology theory. Therefore there is a version of the homology groups called \textbf{reduced} homology groups $\tilde{H_n}$ where $\tilde{H}_n(X) = H_n(X)$ for all $n \in\N^+$ and $\tilde{H}_n \oplus \mathbb{Z} = H_n(\Z)$. This means that the $0$-th reduced homology group of a one point space the trivial group is instead of $\mathbb{Z}$.
A detailed derivation of the reduced groups can be found in \cite[p. 110]{hatcher}.

%TODO: change this definition to an arbitrary index set
\begin{defin}
  Let $G_1, \ldots, G_n$ be abelian groups for $n \in \N$. Then the \textbf{external direct sum} of the groups is defined as
  \begin{equation*}
    G_1 \oplus \cdots \oplus G_n = \bigoplus_{i=1}^n G_i = \prod_{i=1}^n G_i.
  \end{equation*}
  This is again an abelian group with the operation \[g \cdot h = (g_1 \cdot_{G_1} h_1, \ldots, g_n \cdot_{G_n} h_n)\] for $g,h \in \bigoplus_{i=1}^n G_i$.
  If $f_1, \ldots, f_n$ are homomorphisms with \[f_i\colon G_i \to H_i\] where $H_i$ are abelian groups for $i = 0,\ldots,n$. Then
  \begin{equation*}
    \bigoplus_{i=1}^nf_i\colon \bigoplus_{i=1}^n G_i\to \bigoplus_{i=1}^nH_i,\: g \mapsto (f_1(g_1),\ldots, f_n(g_n))
  \end{equation*}
  is a homomorphisms.
\end{defin}

\begin{defin}
  Let $X$ be a topolgical space and let $A \subseteq X$ be a non-empty closed subspace, that is a deformation retract of a neighborhood in $X$. Then $(X, A)$ is a \textbf{good pair}.
\end{defin}

\begin{lemma}\label{lem:holwe}
  Let $X_\alpha$ be a sequence of topological spaces with basepoints $x_\alpha\in X_\alpha$ and let $\iota_\alpha\colon X_\alpha \to \bigvee\limits_{\alpha \in I}X_\alpha$ for $\alpha \in I$ where $I$ is an arbitrary index set such that $(X_\alpha, x_\alpha)$ are good. Then it holds that the maps $\iota_\alpha$ induce an isomorphism
  \begin{equation*}
    \bigoplus_{\alpha \in I}H_n(\iota_\alpha) \colon \bigoplus\limits_{\alpha\in I} \tilde{H}_n(X_\alpha)\to \tilde{H}_n\left(\bigvee\limits_{\alpha\in I} X_\alpha\right).
  \end{equation*}
\end{lemma}

\begin{proof}
  See \cite[Corollary 2.25]{hatcher}.
\end{proof}

Proofs in the later sections will only involve reasoning about homology groups. Their is a dualized concept of homology called cohomology.
The dualization in the sense of category theory works be replacing the homology groups in the chain complex by $\underline{\rm Grp}(H_n(X); G)$ where $G \in \underline{\rm Ab}$ is an abelian group. There is no need to also develop the theory of cohomology in this thesis nor a need to use it later in the proofs because of the following result. Its called \textbf{Alexander duality} and connects homology and cohomology groups.

% TODO: check and insert the correct version of alexanders duality here
% in the prove of the lemma in section 6 the reference goes into spanier
% but it is unclear how the duality is used and which version is referenced
\begin{thm}\label{thm:alex}
  Let $n \in \N$ and $p \in \mathbb{P}$. If $A \subseteq \mathbb{S}^n$ is a compact, non-empty and contractible subspace then
  \begin{equation*}
    \tilde{H}_k(\mathbb{S}^n \setminus A) \cong \tilde{H}^{n-k-1}(A)
  \end{equation*}
  for all $q \in \N$.
\end{thm}

\begin{proof}
  
\end{proof}

\subsection{Theorem of Mayer-Vietoris}
Often we can calculate the homology of simple subspaces of a larger space and want to deduce the homology of the larger space from them.
This can be accomplished with the \textbf{Mayer-Vietoris-Sequence} which is a homological version of the \textbf{Van Kampen-Theorem} (see \cite[Chapter 1.2]{hatcher}).

\begin{defin}
  Let $(G_n)_{n\in\N}$ be a sequence of abelian groups and let $(\varphi_n)_{n\in\N}$ be a sequence of homomorphisms such that
  \begin{equation*}
    \varphi_n\colon G_n \to G_{n-1}
  \end{equation*}
  for $n \in \N^+$ and $\varphi_0\colon G_0 \to 0$.
  The sequence is called \textbf{exact} if
  \begin{equation*}
    \im\varphi_{n+1} = \ker\varphi_n.
  \end{equation*}
  for all $n \in \N$.
  An exact sequence of the form
  \begin{equation*}
    0 \to A \to B \to C \to 0
  \end{equation*}
  that is exact is called a \textbf{short exact sequence}.
\end{defin}

\begin{thm}\label{thm:mvs}
  Let $X$ be a topological space and let $A, B \subseteq X$ subspaces of $X$ such that \[X = \dot{A} \cup \dot{B}, \: A \cap B \neq \emptyset.\]
  The \textbf{Mayer-Vietoris-Sequence}
  \begin{equation*}
    \ldots \to H_n(A\cap B) \overset{\Phi}{\to} H_n(A) \oplus H_n(B) \overset{\Psi}{\to} H_n(A \cup B) \overset{\partial}{\to} H_{n-1}(A\cap B) \to \ldots \to 0
  \end{equation*}
  is an exact sequence where the mappings $\Phi$ and $\Psi$ are defined as
  \begin{align*}
    &\Phi\colon H_n(A\cap B) \to H_n(A) \oplus H_n(B),\: z + B_n(A\cap B) \mapsto (z+B_n(A), -z + B_n(B)), \\
    &\Psi\colon H_n(A) \oplus H_n(B) \to H_n(A\cup B), \: (z_1+ B_n(A), z_2 + B_n(B)) \mapsto (z_1 + z_2) + B_n(A \cup B).
  \end{align*}
\end{thm}

\begin{proof}
  For a detailed derivation of this Theorem look at \cite[p. 149]{hatcher}. 
\end{proof}

% Example Homology group of sphere
\begin{ex}
  The homology group of the $n$-dimensional sphere $\mathbb{S}^n$ are as follows
  \begin{equation*}
    H_k(\mathbb{S}^n) \cong \begin{cases}
      0, &n \neq k, \\
      \mathbb{Z}, &n = k,
    \end{cases}
  \end{equation*}
  for $k \in \Z$.
\end{ex}

\begin{proof}
  Let $A$ be the upper hemisphere and $B$ the lower hemisphere of $\mathbb{S}^n$. Then $A\cap B = \mathbb{S}^{n-1}$. Consider the Mayer-Vietoris sequence of this decomposition
  \begin{equation*}
    \ldots \overset{\partial'}{\to} H_k(\mathbb{S}^{n-1}) \to H_k(A) \oplus H_k(B) \to H_k(\mathbb{S}^n) \overset{\partial}{\to} H_{k-1}(\mathbb{S}^{n-1}) \to \ldots \to 0.
  \end{equation*}
  Since $A$ and $B$ are contractible it follows that $H_n(A) \cong H_n(B) \cong 0$ for all $n \in N$. This means that
  \begin{align*}
    0 &= \im \Psi = \ker \partial_k \\
    H_k(\mathbb{S}^{n-1}) &= \ker \Phi = \im \partial_{n+1}.
  \end{align*}
  We get that the maps $\partial\colon H_k(\mathbb{S}^n) \to H_{k-1}(\mathbb{S}^{n-1})$ are isomorphism. And thus with the fact that $H_1(\mathbb{S}^1) \cong \Z$ the claim is proven by induction on $k$.\footnote{The fact that the first homology group of $\mathbb{S}^1$ is isomorphic to $\Z$ can easily be proven with another type of homology, namely simplicial homology \cite[p. 106]{hatcher}. And since the singular and simplicial homology groups are isomorphic for triangulable spaces it can be deduced that $H_1(\mathbb{S}^1) \cong \Z$ also in the singular case. A triangulation of $\mathbb{S}^1$ is the graph circle graph three vertecies.}
\end{proof}
